\Large \bf Uncovering Distributed System Bugs during Testing (not Production!)

### 2015-08-24 casestudies.tex
Added small description of Fabric.

Draft.

>>>>

\emph{Azure Service Faric} (or \emph{Fabric} for short)
is a platform and API for creating reliable services
that execute on a cluster of machines.
The developer writes a service that receives requests (e.g.\ from some client program via HTTP)
and mutates its state based on these requests.
In order to make the service \emph{reliable},
Fabric launches several copies (\emph{replicas}) of the service,
where each copy runs as a separate process
on different nodes in the cluster.
One replica is selected to be the \emph{primary}
which serves client requests; the rest are \emph{secondaries}.
The primary replicates state changes to the secondaries
so that all replicas eventually have the same state.
If the primary fails (e.g.\ if the node on which the primary is running crashes),
Fabric elects one of the secondaries to be the new primary
and launches another secondary;
the new secondary will receive a full or partial copy (depending on whether persistent storage is used) 
of the state of the new primary in order to ``catch up'' with the other secondaries. 
Fabric provides a name-resolution service so that clients can always find the current primary.
Fabric exposes several different APIs that developers can use to write services.
